Jeff Goldsmith

### 2019-06-09 software.Rmd
add tidyfun to software

>>>>

## `tidyfun`

Together with Fabian Schiepl, I am an author of the [`tidyfun`](https://fabian-s.github.io/tidyfun/) package. This package seeks to provide accessible and well-documented software that **makes functional data analysis in `R` easy** – specifically data wrangling and exploratory analysis.

The `tidyfun` webpage includes several illustrative vignettes, and [this short overview](tidyfun.html) is a quick place to get started.
